---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Coinprofile

The main goal of Coinprofile is to build the 
  coincident profile according to Martinez, Nieto, and Poncela (2016) 
  \url{https://www.sciencedirect.com/science/article/pii/S0167715215003764}.
  This methodology studies the relationship between a couple of
  time series based on the the set of turning points of each
  time series. To calculate the 
  turning points we use Bry and Boschan (1971) 
  methodology. The coincident profile establishes if two time
  series are coincident, or one of them leads the second.
## Installation

You can install the released version of Coinprofile from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Coinprofile")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Coinprofile)
## basic example code
set.seed(123)
w <- seq(-3, 7, length.out = 100)
x1 <- sin(pi*w)+rnorm(100,0,0.1)
x2 <- sin(pi*w-0.1)+rnorm(100,0,0.1)
coincident_profile(x1, x2, 4, 5, "name.x", "name.y", TRUE, 1991, 2015, 4, 4)
```

## In this example x leads y three periods

```{r example}
set.seed(123)
w <- seq(-3, 7, length.out = 100)
x <- sin(pi*w)+rnorm(100,0,0.1)
y <- sin(pi*w-1)+rnorm(100,0,0.1)
coincident_profile(x, y, 4, 6, "name.x", "name.y", TRUE, 1991, 2015, 4, 4)

```

